Enrich the datasets with new columns.

### 2020-11-09 inst/analysis/enrich_dataset.Rmd
Move to .4 dataset

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      # record the current time before each chunk
      now <<- Sys.time()
    } else {
      # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res, unit(res))
    }
  }
}))

@@

now <- Sys.time()

library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)
library(DT)
library(fst)
library(fs)
library(parallel)

@@

```{r ast_size}
#eval_calls <- eval_calls %>% add_ast_size()
```

@@

```{r}
eval_calls_ast_size <- eval_calls_corpus %>% select(eval_call_srcref, caller_package, caller_function, eval_source_type, expr_resolved_nodes, nb_ev_calls)

write_fst(eval_calls_ast_size, path(RUN_TRACE_DIR, "summarized-ast-size.fst"))
```

@@

```{r}
max_call_sites <- max(call_sites_per_package$n)
r("max call sites enrich")
```

@@

```{r write_back}
write_fst(undefined_per_package, PACKAGE_EVALS_UNDEFINED_FILE)

>>>>

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      # record the current time before each chunk
      now <<- Sys.time()
    } else {
      # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res, units(res))
    }
  }
}))

@@

now <- Sys.time() 
library(tidyverse)
library(stringr)
library(viridis)
library(vctrs)
library(DT)
library(fst)
library(fs)
library(parallel)

@@

@@

```{r}
# Used when using dataset 2 which has incorrect AST sizes.

#eval_calls_ast_size <- eval_calls_corpus %>% select(eval_call_srcref, caller_package, caller_function, eval_source_type, expr_resolved_nodes, nb_ev_calls)

#write_fst(eval_calls_ast_size, path(RUN_TRACE_DIR, "summarized-ast-size.fst"))
```

@@

```{r}
max_call_sites <- max(call_sites_per_package$n)
r("max call sites enrich", max_call_sites)

one_call_sites <- nrow(call_sites_per_package %>% filter(n == 1))
r("one call sites enrich", one_call_sites)

no_call_sites <- nrow(call_sites_per_package %>% filter(n == 0))
r("no call sites enrich", no_call_sites)
```

@@

```{r write_back}
write_fst(undefined_per_package, EVALS_UNDEFINED_FILE)
